Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS

### 2023-08-30 paper/ms.tex
Update ms (JNW comments) - results
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

%FIXME TODO LEFT OFF HERE
\subsubsection{Counting dips}
\label{subsec:counting}

@@

Wrapping is necessary to eliminate edge
effects when fitting the light curve and when identifying local minima
in the residuals.  A phased light curve would usually cover phases
$\phi \in [ 0,1 ]$.  We instead performed the entire preceding
procedure over a phase-folded light curve spanning $\phi \in [-1,2 ]$,
which was created by duplicating and concatenating the ordinary
phase-folded light curve.  The free parameters we adopted throughout
this analysis -- for instance the maximum number of spline knots per
cycle, and the height and depth criteria for dips -- were chosen
during testing based on the desire to correctly re-identify a large
fraction ($>$90\%) of previously known CRs, while also being able to
consistently reject common false positives such as rapidly rotating
spot-induced variability and typical eclipsing binaries.

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The ``high-quality sample'' includes \ngoods\ objects,
which demonstrated what we viewed as unambiguous characteristics of
the CR phenomenon in at least one TESS sector.  The classification of
\nmaybes\ CR candidates was ambiguous, and the \ndebunked\ remaining
objects were false positives that we discuss below.  The
\texttt{quality} column in the table divides the three classes;
additional data from TESS or other instruments could help resolve the
classification of the ambiguous cases.   Of the \ncqvsnodebunked\ CRs
and candidate CRs, \nbothdipfourier\ were found using both the
dip-counting and Fourier techniques, \nyesdipnofourier\ were found
using only the dip-counting technique, and \nyesfouriernodip\ were
found using only the Fourier technique.  In the following, we will
restrict our discussion to the high-quality sample, irrespective of
discovery method.

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CRs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CR phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CRs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

In terms of the light curve shapes, Figure~\ref{fig:cqvs} shows a
broad range of variability, with anywhere from two to eight local
minima per cycle.  Some stars show relatively ordinary modulation
during one portion of the phased light curve, and highly structured
modulation in the remainder of the cycle (e.g.  TIC~206544316,
TIC~224283342, TIC~402980664).  Others show structured modulation over
the entire span of a cycle (e.g. TIC~2234692, TIC~425933644,
TIC~142173958).  Others show some mix between these two modes.

@@

Of our \ncqvsnodebunked\ confirmed and candidate CRs,
\nnotfieldbanyan\ were associated with a nearby moving group or open
cluster, primarily using BANYAN\,$\Sigma$.\footnote{Two of the
\nnotfieldbanyan\ memberships were made with low confidence and are
flagged in Table~\ref{tab:thetable}.  One membership, of TIC~397791443
in IC\,2602, was made manually from a literature search
\citep[e.g.][]{2020A&A...633A..99C}.}  The relevant groups are listed
in Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CRs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality and youth of that group.  The yield in
Sco-Cen is not surprising since Sco-Cen contains the majority of
pre-main-sequence stars in the solar neighborhood, and many of its
stars were selected for TESS 120-second cadence observations by
various guest investigators.  Given the $\lesssim$$10\%$ completeness
of TESS beyond 100\,pc, there may be many more CRs in Sco-Cen that
remain to be discovered.

For the two stars for which BANYAN\,$\Sigma$ did not find any
association, we were not able to confidently associate either star
with any young groups.  Both do seem to show the CR signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.

@@

The upper age limit for CRs may even pass 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  This group's $200 \pm 50$\,Myr age is
based on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades but younger than the 400\,Myr Ursa Major
moving group.  The formal BANYAN-$\Sigma$ membership probability is
however somewhat low, perhaps due to the missing radial velocity.
This lack of information could be resolved by acquiring even a
medium-resolution spectrum.  An independent assessment of the group's
kinematics using Gaia data, and its rotation sequence using TESS,
could lend further credence in such an analysis.

@@

Most CRs in our catalog did not show infrared excesses in the
$W1$-$W4$ bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$
and $W4$ at $>$3$\sigma$ above the photospheric prediction).

The two sources exhibiting an IR excess were TIC~193136669 (TWA~34)
and TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
($\approx$10\,Myr), and have relatively long periods of 38\,hr and
44\,hr respectively.  In our initial labeling, we labeled both as
``ambiguous'' CRs because the dips in their light curves did not show
the rigid periodicity typical of CRs;  their periods were also
relatively long.  However, inspection of further sectors clarified
that both sources are dippers (see online plots in
Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CR in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CRs and dippers
in light of these ``misclassifications'' .

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CRs identified by our search}.
      CRs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CRs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CR candidates are light blue circles.  Unresolved
      binaries are flagged either if the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CRs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CR periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

The main types of binaries of interest in this work were those that
were unresolved, because they could confuse our understanding of CRs.
For instance, unresolved binaries might produce multiple photometric
signals and hinder our ability to correctly identify the star hosting
the CR signal.  Unresolved binaries could also bias photometric magnitude
and color measurements, which would affect our stellar parameter
estimates.  To attempt to identify binaries, we considered the
following lines of information.

@@

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
color.\footnote{For an explanation of the renormalized unit weight
error (RUWE), see the GAIA DPAC technical note
\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
RUWEs imply excess noise relative to a single-source astrometric
model.  This can be caused by marginally resolved point sources
skewing the single-transit centroid measurements,  intrinsic
photometric variability, or intrinsic astrometric motion.  Based on
this exercise, we adopted a threshold of RUWE$_{\rm DR3}$ $>$ 2 to
flag sources with excess astrometric noise.  This threshold was met
for \ngoodhighruwe/\ngoods\ high-quality CRs;
\nmaybehighruwe/\nmaybes\ of the ambiguous ones had this
characteristic.  There is some subjectivity in where to set the
threshold, since the RUWE distribution has an extended tail
\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CRs
and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
flagged.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bona fide, candidate, and debunked complex rotators from
  the TESS 2-minute data. {\bf For internal review, full versions are
  available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}}
  \label{tab:thetable}}
%\toprule
%\midrule
%\endhead
\startdata
  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
  -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CRs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CRs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
  binarity flag ``Bin'' is for Gaia DR3
  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
  (bit 3).  The machine-readable version, available online, includes
  additional columns for the Gaia DR2 and DR3 source identifiers, as
  well as the stellar parameter uncertainties.  The age uncertainties
  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
  statistical uncertainties on the temperature, radius, and mass are
  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
  any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
	The ``(?)'' string denotes low-confidence membership.
}
\end{deluxetable}

>>>>

\subsubsection{Counting dips}
\label{subsec:counting}

@@

Wrapping is necessary to eliminate edge effects when fitting the light
curve and when identifying local minima in the residuals.  A phased
light curve would usually cover phases $\phi \in [ 0,1 ]$.  We instead
performed the analysis described above using a phase-folded light
curve spanning $\phi \in [-1,2 ]$, which was created by duplicating
and concatenating the ordinary phase-folded light curve.  The free
parameters we adopted throughout the analysis -- for instance the
maximum number of spline knots per cycle, and the height and depth
criteria for dips -- were chosen during testing based on the desire to
correctly re-identify a large fraction ($>$90\%) of previously known
CRs, while also being able to consistently reject common false
positives such as rapidly rotating spot-induced variability and
typical eclipsing binaries.

@@

Table~\ref{tab:thetable} lists the \nallcands\ objects identified by
our search.  The \ngoods\ stars in the ``good'' sample demonstrated
what we deemed to be the key characteristics of the CR phenomenon in
at least one TESS sector.  The classification of \nmaybes\ CR
candidates was ambiguous, and the \ndebunked\ remaining objects were
notable false positives that we discuss below.  The \texttt{quality}
column in the table divides the three classes; additional data from
TESS or other instruments could help resolve the classification of the
ambiguous cases.   Of the \ncqvsnodebunked\ CRs and candidate CRs,
\nbothdipfourier\ were found using both the dip-counting and Fourier
techniques, \nyesdipnofourier\ were found using only the dip-counting
technique, and \nyesfouriernodip\ were found using only the Fourier
technique.  In the following, we will focus our discussion on the good
sample, irrespective of discovery method.  We will often refer to
stars by their TIC identifiers; the easiest way to reference these
against the figures in most document readers is to use a
``find'' ({\tt Ctrl+F}) utility.

Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
\ngoods\ CRs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CR phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CRs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

The light curves show between two and eight local minima per cycle.
Some stars show ordinary sinusoidal modulation during one portion of
the phased light curve, and highly structured modulation in the
remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).  Others show structured modulation over the entire
span of a cycle (e.g. TIC~2234692, TIC~425933644, TIC~142173958).
Others show some mix between these two modes.

@@

Of our \ncqvsnodebunked\ confirmed and candidate CRs,
\nnotfieldbanyan\ were associated with a nearby moving group or open
cluster, primarily using BANYAN\,$\Sigma$.\footnote{Two of the
\nnotfieldbanyan\ memberships were made with low confidence and are
flagged in Table~\ref{tab:thetable}.  The assignment of TIC~397791443
to IC\,2602 was based not on BANYAN\,$\Sigma$ but instead on a
literature search \citep[e.g.][]{2020A&A...633A..99C}.}  The relevant
groups are listed in Table~\ref{tab:thetable}; their ages span
$\approx$5-200\,Myr.  The groups that contain the largest number of
CRs in our catalog are Sco-Cen, Tuc-Hor, and Columba.  Six CRs were
also identified in the Argus association \citep{2019ApJ...870...27Z},
which serves as an indirect line of evidence supporting the reality
and youth of that group.  The large contribution from Sco-Cen is not
surprising since Sco-Cen contains the majority of pre-main-sequence
stars in the solar neighborhood, and many of its stars were selected
for TESS 120-second cadence observations by guest investigators.
Given the $\lesssim$$10\%$ completeness of TESS beyond 100\,pc, there
may be many more CRs in Sco-Cen that remain to be discovered.

There were two stars for which neither BANYAN\,$\Sigma$ nor a
literature search led to a confident association with any young group.
Both stars display CR signals over multiple TESS sectors. Both are
photometrically elevated relative to the main sequence, an indication
of youth.  Both were also noted by \citet{2021ApJ...917...23K} as
being in the ``diffuse'' population of $<$50\,Myr stars near the Sun.

@@

The maximum age of CRs might even exceed 200\,Myr, based on the
candidate membership of TIC~294328887 in the Carina Near moving group
\citep{2006ApJ...649L.115Z}.  The estimated age of this group, $200
\pm 50$\,Myr, is based on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population of stars
older than the Pleiades and younger than the 400\,Myr Ursa Major
moving group.  However, the formal BANYAN-$\Sigma$ membership
probability is somewhat low (only 6\%), perhaps due to the missing
radial velocity.  This lack of information could be rectified by
acquiring even a medium-resolution spectrum.  An independent
assessment of the group's kinematics using Gaia data, and its rotation
sequence using TESS, could also bear on the question of whether
TIC~294328887 is a member.

@@

Most CRs in our catalog did not show infrared excesses in the
$W1$-$W4$ bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$
and $W4$ fluxes are more than 3$\sigma$ above the photospheric
prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).

Both of these stars with IR exceses are in the TW Hydrae association
($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
respectively.  In our initial labeling, we labeled both as
``ambiguous'' CRs because the dips in their Sector~36 light curves
seemed to stochastically evolve over only one or a few cycles, which
is not typical of CRs; their periods were also long in comparison with
most of the other CRs.  Inspection of additional sectors clarified
that both sources are dippers, not CRs (see the online plots in
Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve of
shows completely different behavior from Sector~36, with variability
amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC 57830249
also shows continuum emission at 1.3\,mm \citep{2015A&A...582L...5R},
which suggests that cold dust grains are present.

The dipper classification of TIC~193136669 is less obvious; the main
indication that it is a dipper is that Sectors 62 and 63 show its dips
appearing and disappearing within the span of one cycle.  None of the
CRs in our sample exhibit this property.  Independently, TIC~193136669
is known to have a cold disk of dust and molecular gas, based on
1.3\,mm continuum emission and resolved $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CR in Table~\ref{tab:thetable}.
Section~\ref{subsec:discdippers} highlights plausible evolutionary
connections between CRs and dippers in light of these
``misclassifications''.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CRs identified by our search}.
      CRs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CRs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CR candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CRs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CR periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

The main types of binaries of interest in this work were those that
were unresolved, because they can lead to misinterpretations of the data.
For instance, unresolved binaries might produce multiple photometric
signals and hinder our ability to correctly identify the star hosting
the CR signal.  Unresolved binaries could also bias photometric magnitude
and color measurements, which would affect our stellar parameter
estimates.  To attempt to identify binaries, we considered the
following lines of information.

@@

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
color.\footnote{For an explanation of the renormalized unit weight
error (RUWE), see the GAIA DPAC technical note
\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
RUWEs imply excess astrometric noise relative to a single-source
model.  This can be caused by marginally resolved binaries,  intrinsic
photometric variability, or intrinsic astrometric motion.  Based on
this exercise, we adopted a threshold of RUWE$_{\rm DR3}$ $>$ 2 to
flag sources with excess astrometric noise.  This threshold was met
by \ngoodhighruwe/\ngoods\ high-quality CRs and by
\nmaybehighruwe/\nmaybes\ of the ambiguous CRs.  The choice of the threshold RUWE
is somewhat subjective, since the RUWE distribution has an extended tail
\citep[e.g.][]{2022MNRAS.513.5270P}.  If we had instead required
RUWE$_{\rm DR3}$ $>$ 1.4, \ngoodweakruwe/\ngoods\ high-quality CRs
and \nmaybeweakruwe/\nmaybes\ of the ambiguous sample would have been
flagged.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bona fide, candidate, and debunked complex rotators from
  the TESS 2-minute data. {\bf For internal review, full versions are
  available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}}
  \label{tab:thetable}}
%\toprule
%\midrule
%\endhead
\startdata
  TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & $P_{\rm sec}$ & Quality & Bin & $N_{\rm sector}$ \\
  -- &   mag & pc &    mag &      -- &        hr &   -- &        Myr &  K                  & $R_\odot$ & $M_\odot$ & $R_\star$         & hr                     & -- & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ good CRs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CRs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The three-bit
  binarity flag ``Bin'' is for Gaia DR3
  \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
  \texttt{ruwe} outliers (bit 2), and stars with multiple TESS periods
  (bit 3).  The machine-readable version, available online, includes
  additional columns for the Gaia DR2 and DR3 source identifiers, as
  well as the stellar parameter uncertainties.  The age uncertainties
  are typically $\approx \pm 10\%$, but can be asymmetric.  The median
  statistical uncertainties on the temperature, radius, and mass are
  $\pm$50\,K, $\pm$4\% and $\pm$9\% respectively.
  $N_{\rm sector}$ denotes the number of TESS sectors for which {\it
  any} data are expected to be acquired between July~2018 and
  Oct~2024.  This number is generally greater than the number of
  sectors for which 120-second cadence data exist.   Association names
  and provenance follow conventions adopted by
  \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
	The ``(?)'' string denotes low-confidence membership.
}
\end{deluxetable}
